Cyclone: High Availability for Persistent Key Value Stores

### 2017-11-17 paper/paper.tex
Updates.

\documentclass[pageno]{jpaper}

%replace XXX with the submission number you are given from the ASPLOS submission site.
\newcommand{\asplossubmissionnumber}{387}

\usepackage[normalem]{ulem}
\usepackage{parskip}

@@

\title{\Large \bf Cyclone: High Availability for Persistent Key Value Stores}

@@

Cyclone uses the RAFT consensus protocol~\cite{raft} to keep the logs in sync
across the replicas. On failure of the leader replica, a new leader is
automatically elected -- RAFT ensures that the new leader has the most up to
date log. The Cyclone client library automatically locates the new leader on a
failover, resulting in only a brief interruption in service for
clients. Although read requests (GET operations) are not logged, they are
serviced in FIFO order with the write requests (PUT/DELETE operations) in
Cyclone's log at the moment the read request is received.

Cyclone provides the following guarantees to clients:

\begin{itemize}
\item Every acknowledged update is applied
\item Every key sees the same sequence of updates across all replicas
\item A client sees a monotonically extending prefix of the sequence of updates
  to any key at that always includes its own updates
\end{itemize}

RAFT ensures that the set of committed updates to any key is in the same order
as in the log, satisfying the first two conditions. For the last condition,
clients maintain the term of the RAFT leader locally and ensure they always talk
to a (possibley different) RAFT leader that has at least the same term. This
helps us avoid split brain problems where a network partitions allows clients to
talk to old RAFT leaders after having committed changes to a new RAFT leader.

We do not provide linearizable reads, although that can be easily supported by
logging the read and running conensus on it like a regular mutation operation.
Finally, Cyclone allows operations to multiple keys in an atomic batch, where
either all updates in the batch are applied or no operation in the batch is
applied, regardless of failures. We also use a lightweight batched operation to
support snapshots.

@@

The first question we deal with is -- how do Cyclone clients decide which
physical log to send a request to? The guarantees from Cyclone cover ordering of
updates to a single key (Section~\ref{sec:sysarch}). They can be satisfied by
ensuring that all reads and writes to a key go to the same physical log
(i.e. RAFT instance). We achieve this by hashing the key to select the physical
log.

@@

\subsection{Ganged Operations}
Supporting batched updates to multiple keys that map to different physical logs
requires a ganged operation across those logs such that all the operations
complete together even in the face of failures. One option is to have an
external co-ordinator run a distributed transaction using two phase commit. In
addition to requiring extra external resources to host the co-ordinator one must
also worry about failure recovery. This also requires two round trips to the
leader to complete what should have been a single batched write request from a
client that is stateless and allowed to fail - such as with key value stores
like Rocksdb~\cite{rocksdb}. We therefore describe a simpler and more performant
solution called ``ganged operations" in Cyclone. Ganged operations allow a
stateless client to issue a batch of update operations as a ``gang",
simultaneously and atomically updating a batch of keys in a single call.

@@

\section{Conclusion}
Cyclone shows how one can leverage a small amount of non-volatile memory to
address two fundamental difficulties in adding high availability to persistent
key value stores. First, Cyclone avoids
paying the cost of the block IO interface for every update operation. This
removes block IO latency from the task of appending updates to the log as well
as sending it out over the network for replication. In turn, this enables us to
apply software packet switching techniques and concurrency to improve the
performance of replication, and making full use of available resources when
replicating log entries over the network. By optimizing the storage and network
components simultaneously, Cyclone enables high availability to persistent key
value stores without compromising on their performance.
\newcommand\myurl[2]{\url{#1}}
\bibliographystyle{plain}
\bibliography{paper}

>>>>

\documentclass[twocolumn]{article}

\usepackage[normalem]{ulem}
\usepackage{parskip}
\usepackage{pdfpages}
\usepackage{url}

@@

\title{Cyclone: High Availability for Persistent Key Value Stores}
\author{Amitabha Roy \and Subramanya R. Dulloor}

@@

Cyclone uses the RAFT consensus protocol~\cite{raft} to keep the logs in sync
across the replicas. On failure of the leader replica, a new leader is
automatically elected -- RAFT ensures that the new leader has the most up to
date log. The Cyclone client library automatically locates the new leader on a
failover, resulting in only a brief interruption in service for
clients.  Cyclone guarantees that the order of operations to any key are linearizable. 
A key sees the exact same sequence of update operations (including deletes) 
on all replicas. These per-key guarantees follow immediately from the 
properties of the RAFT log and by requiring clients to perform a quorum read (logged
as an entry in the RAFT log).

In addition, Cyclone also provides clients with a weak read that does not require a 
quorum read thereby requiring only one round trip to a server.  A weak read of a key sees a prefix of the linearizable history of a key that 
includes all successful update operations made by the client before it issues the 
weak read. To do a weak read, 
clients maintain the last known term of the RAFT leader locally and ensure they always talk
to a RAFT leader that has at least the same term. This ensures that clients see their own writes
avoiding split brain problems where a network partitions allows clients to
talk to old RAFT leaders after having committed changes to a new RAFT leader. In addition, a weak read waits until all pending RAFT log entries have been committed and applied before executing. This ensures that in the event of a failover, any previous committed updates from the same client have been applied and are visible to the weak read. A weak read is not linearizable as the RAFT leader responding to the weak read might actually no longer be the leader - a new one having been elected 
without it realizing, perhaps due to a network partition. This means that while a weak read from a client sees its own writes in this (perhaps pathological) case it might not see later writes by other clients.

Finally, Cyclone allows operations to multiple keys in an atomic batch, where
either all updates in the batch are applied or no operation in the batch is
applied - a property that holds \emph{at all replicas}, regardless of failures. We also use a lightweight batched operation to support snapshots. We discuss how batched operations are implemented later in the paper.

@@

The first question we deal with is -- how do Cyclone clients decide which
physical log to send a request to? The guarantees from Cyclone (except batched
writes)  cover ordering of
updates to a single key (Section~\ref{sec:sysarch}). They can be satisfied by
ensuring that all reads and writes to a key go to the same physical log
(i.e. RAFT instance). We achieve this by hashing the key to select the physical
log.

@@

\subsection{Ganged Operations}
Supporting batched updates to multiple keys that map to different physical logs
requires a ganged operation across those logs such that all the operations
complete together even in the face of failures. One option is to have an
external co-ordinator run a distributed transaction using two phase commit. This
requires extra external resources to host the co-ordinator what should have been a single batched write request from a
client that is stateless and allowed to fail - such as with key value stores
like Rocksdb~\cite{rocksdb}. This also 
requires two round trips to the
leader to complete  We therefore describe a simpler and more performant
solution called ``ganged operations" in Cyclone. Ganged operations allow a
stateless client to issue a batch of update operations as a ``gang",
simultaneously and atomically updating a batch of keys in a single call. This preserves
the system architecture of existing deployments of single image key value store such as Rocksdb.

@@

\section{Conclusion}
Cyclone shows how one can leverage a small amount of non-volatile memory to
address two fundamental difficulties in adding high availability to persistent
key value stores. First, Cyclone avoids
paying the cost of the block IO interface for every update operation. This
removes block IO latency from the task of appending updates to the log as well
as sending it out over the network for replication. In turn, this enables us to
apply software packet switching techniques and concurrency to improve the
performance of replication, and making full use of available resources when
replicating log entries over the network. By optimizing the storage and network
components simultaneously, Cyclone enables high availability to persistent key
value stores without compromising on their performance.

Cyclone is available as open source software at:\\
\url{https://github.com/sdulloor/cyclone/}
\newcommand\myurl[2]{\url{#1}}
\bibliographystyle{plain}
\bibliography{paper}
